---
title: "PSTAT 131 Final Project - Sloth Species"
author: 'Mirabelle Le'
output: html_document
date: '2022-05-31'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The goal of this project is to generate a model that will predict if a sloth is two-toed or three-toed and look at their species.

## All Things Sloths!

If you don't know what sloths are, they are an adorable species of animals well known for being slow and lethargic. These creatures spend a majority of their lives hanging on trees, sleeping, and remaining hidden from predators. The animals live solitary lives and travel from tree to tree using canopy vines. Located in places such as Brazil and Panama, this strange and wonderful animal needs healthy forests to survive. 

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
